\documentclass[letter,12pt]{article}
\usepackage{TLCresume}
\begin{document}

\subsection{Customer Success Engineer \hfill Mar 2025 --- Present}
\subtext{Tailscale \hfill California, United States (Hybrid)}
\begin{zitemize}
\item{Drive technical enablement for enterprise customers deploying Tailscale across hybrid cloud environments, GPU training clusters, and CI/CD pipelines. Architect solutions for complex networking scenarios involving Kubernetes operators, NAT connectors, and subnet routing configurations.}
\item{Troubleshoot critical connectivity issues for high-value customers, analyzing infrastructure, network failures, and firewall configurations. Resolve escalations involving DNS, BGP, and Proxy deployments in production environments.}
\item{Translate customer feedback into actionable feature requests for engineering teams, documenting use cases for Kubernetes resources, routing scenarios, and workload identity federation. Influence product roadmap through structured technical requirements gathering.Serve as technical liaison for enterprise deployments at scale.}
\end{zitemize}

\subsection{Customer Reliability Engineer \hfill Jun 2024 --- Mar 2025}
\subtext{Isovalent/Cisco \hfill Milpitas, CA}
\begin{zitemize}
\item{Proactively managed Cilium Enterprise reliability in production, reducing operational risks and improving performance for major clients such as OpenAI, Palentir, Databricks, and Capital One.}
\item{Collaborated with Solutions Architects and Engineering to resolve customer incidents, streamline documentation, and optimize Kubernetes and networking practices across large-scale environments.}
\item{Conducted production readiness reviews and developed automated customer reproduction environments, utilizing Kubernetes, Linux, and networking expertise to ensure reliability at scale.}
\item{Enhanced troubleshooting efficiency by creating knowledge base articles and automating monitoring, enabling quicker resolution times and supporting Kubernetes-based architectures.}
\end{zitemize}


\subsection{Platform Engineer \hfill Jun 2023 --- Jun 2024}
\subtext{Hyatt Corporation \hfill Chicago, IL}
\begin{zitemize}
\item{Spearheaded the development and implementation of microservice architecture strategies, collaborating closely with development teams to ensure optimal design and scalability.}
\item{Engineered custom tooling for networking practices, reducing customer latency and enhancing developer simplicity, leveraging technologies such as Persistent Storage, Layer 3-7 load balancers, Kubernetes Proxy, and DNS methodologies.}
% \item{Mentored and up-leveled development teams on Kubernetes workloads and pipeline practices through learning seminars and office hours, fostering a culture of continuous learning and improvement.}
\item{Streamlined networking architecture for incoming CDN traffic, resulting in expedited F5 pool changes and automated change requests, enhancing operational efficiency.}
\item{Developed and implemented monitoring techniques utilizing Datadog across platform teams, ensuring adherence to SLO agreements and proactive maintenance of systems.}
\end{zitemize}


%====================
% EXPERIENCE A
%====================
\subsection{DevOps Engineer \hfill May 2021 --- Jun 2023}
\subtext{Casey's General Stores, Inc \hfill Ankeny, IA}
\begin{zitemize}
\item{Leveraged APIs to automate certain networking-based tasks, improving deployment efficiency, and tightly integrating with company resources. This involved utilizing containerization and Azure cloud development.}
\item{Identified store network infrastructure vulnerabilities by monitoring Palo Alto and Cisco Meraki systems, resulting in improved network stability and reduced store downtime.}
\item{Conducted resource utilization and capacity planning. This prevented downtime and ensured a seamless customer experience.}
\item{Transformed company-wide asset management and discovery using this system, eliminating manual & error-prone bookkeeping. Discovered roughly 22,000 previously unknown network devices, allowing potential tax write offs up to \$2,200,000.}
\item{Implemented an agile approach to the deployment of an on premises OpenShift Kubernetes environment, collaborating with team members to iteratively refine the process and continuously improve efficiency and quality.}
\end{zitemize}
% %====================
% % EXPERIENCE C
% %====================
% \subsection{{IT Specialist \hfill MAY 2017 --- Dec 2022}}
% \subtext{Singh360 \hfill Medina, MN}
% \begin{zitemize}
% \item{Led small business IT operations and management, including the installation of networking infrastructure, hardware/software deployment, and software solutions management.}
% \item{Managed the full IT life-cycle for all hardware assets, ensuring optimal performance and longevity.}
% \item{Conducted comprehensive vulnerability assessments and penetration tests to secure the perimeter network, systems, and applications.}
% \end{zitemize}

%====================
% EXPERIENCE D
%====================
% \subsection{{Crypto Block-Chain Transaction Validation \hfill SEP 2019 --- Present}}
% \subtext{Ethereum Network \hfill }
% \begin{zitemize}
% \item  {Utilizing the use of Graphics Processing Units for securing transactions on Ethereum's Proof of Work consensus mechanism.}
% \item{Developed knowledge and understanding in proper server hardware efficiency/management.}
% \end{zitemize}






%====================
% EXPERIENCE E
%====================
%\subsection{{ROLE / PROJECT E \hfill MMM YYYY --- MMM YYYY}}
%\subtext{company E \hfill somewhere, state}
%\begin{zitemize}
%\item In lobortis libero consectetur eros vehicula, vel pellentesque quam fringilla.
%\item Ut malesuada purus at mi placerat dapibus.
%\item Suspendisse finibus massa eu nisi dictum, a imperdiet tellus convallis.
%\item Nam feugiat erat vestibulum lacus feugiat, efficitur gravida nunc imperdiet.
%\item Morbi porta lacus vitae augue luctus, a rhoncus est sagittis.
%\end{zitemize}

\end{document}